EDA

### 2020-02-28 src/draft.Rmd
reference added

Elastic net
```{r}
library(caret)
tibble::as_tibble(test)
cv_5 = trainControl(method = "cv", number = 5)
ridge = train(
  rate_pct ~ Year + Municipalities + TaxClassCode + assessTotal_pct + tax, data = test,
  method = "glmnet",
  trControl = cv_5
)
ridge
```
apha = 1 which implies lasso! refer to lasso.

>>>>

Elastic net: 
reference: https://daviddalpiaz.github.io/r4sl/elastic-net.html
```{r}
library(caret)
tibble::as_tibble(test)
cv_5 = trainControl(method = "cv", number = 5)
ridge = train(
  rate_pct ~ Year + Municipalities + TaxClassCode + assessTotal_pct + tax, data = test,
  method = "glmnet",
  trControl = cv_5
)
ridge
```
apha = 1 which implies lasso! refer to lasso.
